\documentclass{mla}

% Header
\firstname{Jerred}
\lastname{Shepherd}
\professor{Dr. Brown}
\class{ENG 211-04}
\title{Outline of The advantages of self-driving cars over traditional cars}

\begin{document}
\makeheader
Thesis: Self-driving cars present a host of advantages compared to traditional cars and will overall be beneficial to humans especially when they are widely adopted.

\begin{enumerate}
	\item Self-driving cars are on the road today, they aren't some abstract concept yet to be realized.
	\begin{enumerate}
	    \item The technology is advancing very rapidly.
	    \item List figures showing how many self-driving cars are on public roads in the United States (or a similar figure)
	\end{enumerate}
	
	\item Cars today already leverage the power of computers while driving
	\begin{enumerate}
	    \item List the levels of driving automation
	    \item Give figure of cars today that use some form of computer-assisted driving
	\end{enumerate}
	
	\item Self-driving cars have the potential to revolutionize not only transportation, but also society.
	\begin{enumerate}
	    \item Demonstrate how widely effected we are by transportation.
	    \begin{enumerate}
	        \item Culture
	        \item Jobs
	    \end{enumerate}
	    \item Dive into the effects of previous transportation-related revolutions, such as couriers in ancient Persia, horses, trains, cars, etc.
	\end{enumerate}
	
	\item Driving a car is inherently dangerous
	\begin{enumerate}
	    \item The driver must know and obey traffic laws
	    \item A lapse in the driver's attention can prove fatal
	    \item Human reaction speed is limited
	    \item Human judgement in stressful situations may not be ideal
	    \item Other drivers on the road have the same caveats
	\end{enumerate}
	
	\item Automating the task of driving can help mitigate the limitations of humans.
	\begin{enumerate}
	    \item A computer cannot be distracted
	    \item Judgement is absolute; stress will not effect performance
	    \item Does not require a trained operator
	\end{enumerate}
	
	\item Self-driving cars will allow humans to focus on more interesting tasks.
	
	\item A culture shift could occur through the adoption of self-driving cars
	\begin{enumerate}
	    \item Ride services such as Uber, Lyft, etc. have already begun to reduce the need for car ownership in major cities
	    \item Self-driving cars can help to further reduce the need
	\end{enumerate}
\end{enumerate}
\end{document}
