%-------------------------
% Resume in Latex
% Author: Sourabh Bajaj, modified by Jerred Shepherd
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{hyperref}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Jerred Shepherd} & Email: \href{mailto:root@sjer.red}{root@sjer.red}\\
  \href{https://sjer.red}{https://sjer.red} & GitHub: \href{https://github.com/shepherdjerred}{https://github.com/shepherdjerred}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science (OMSCS, Part-time)}{August 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Coursework}{Distributed Systems, Compilers, Advanced Operating Systems}
      \resumeItemListEnd
    \resumeSubheading
      {Harding University}{Searcy, AR}
      {Bachelor of Science in Software Development}{August 2015 -- May 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Pinterest}{Seattle, WA}
    {Software Engineer II}{September 2024 - Present}
    \resumeItemListStart
      % Scale: thousands of studies/experiments active at any time, each operating on millions of users
      % Platform influences hundreds of millions of dollars of ad revenue
      \resumeItem{Measurement Hub}{Leading frontend migration of advertiser measurement platform from 10-year-old POC to production-grade system, directing 5 engineers across thousands of experiments and millions of users. Achieved 99\% report reliability (up from 50\%). Used LLMs extensively for implementation, design docs, and bug fixes.}
      \resumeItem{Engineering influence}{Set frontend patterns adopted by 30 engineers across 4 teams: strong typing, validation at boundaries, integration testing, and accessibility.}
      \resumeItem{Conversion Lift}{Owning end-to-end migration of Pinterest Conversion Lift as sole technical lead. Driving API schema adoption (previously untyped) and database normalization from JSON blob to relational model. Directing 3 engineers across full-stack implementation.}
      \resumeItem{AI tooling \& adoption}{Built internal tools giving LLMs safe access to internal systems and data. Drove org-wide AI adoption through presentations and hands-on enablement. Authored coding agent skills, guidelines, and CLI tools automating oncall. Established static analysis guardrails for AI-assisted development.}
    \resumeItemListEnd

    \resumeSubheading
      {Posit Software}{Remote}
      {Software Engineer}{September 2021 - June 2024}
      \resumeItemListStart
        \resumeItem{Frontend}{Led rewrite of Package Manager frontend to Vue 3 \& TypeScript, cutting 70\% of dependencies and 90\% of bundle size. Led UI redesign improving first-use experience and accessibility.}
        \resumeItem{Testing infrastructure}{Designed containerized framework enabling isolated local testing of any component.}
        \resumeItem{macOS cross-compiler}{Built cross-compiler toolchain targeting arm64 macOS on Kubernetes. Guided team to production, enabling R package builds with C/C++/Fortran/Rust.}
        \resumeItem{Developer experience}{Shortened feedback loops by speeding up CI and dev environments. Set up automated linters, formatters, and dependency updates.}
        \resumeItem{Backend}{Built Go backend APIs for authentication token generation. Migrated to portable static binary, simplifying deployment across Linux/macOS.}
      \resumeItemListEnd

    \resumeSubheading
      {Amazon Web Services}{Seattle, WA}
      {Software Development Engineer}{July 2019 - August 2021}
      \resumeItemListStart
        \resumeItem{Backend}{Implemented features using distributed state machine with DynamoDB, SQS, Lambda, S3. Optimized fleet configuration for 66\% reduction in server costs.}
        \resumeItem{Process automation}{Built tool to automatically root-cause issues using metrics and logs, reducing weekly manual effort from 4 hours to minutes.}
        \resumeItem{Operations}{On-call for service managing tens of millions of EC2 instances at thousands of requests per second. Root-caused incidents and resolved customer issues.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Skills}
  TypeScript, Go, Java, Python, SQL, React, Vue, Astro, Bun, Kubernetes, Docker, AWS

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://clauderon.com}{Clauderon}}{A session manager for AI coding agents (Claude Code, Codex, Gemini). Daemon architecture enables controlling all sessions from native apps (iOS, macOS) or web, with isolated Docker/K8s execution and zero-credential security.}
    \resumeSubItem{\href{https://github.com/shepherdjerred/monorepo/tree/main/packages/homelab}{Kubernetes Homelab}}{A k3s cluster running on hardware at my home. Managed with cdk8s and ArgoCD.}
    \resumeSubItem{Compiler}{Implemented a compiler from scratch for the Tiger language targeting MIPS assembly.}
    \resumeSubItem{Paxos}{Implemented the Paxos consensus algorithm from scratch.}
    \resumeSubItem{\href{https://github.com/shepherdjerred/monorepo/tree/main/packages/castle-casters}{Game Engine}}{Cross-platform Java game with OpenGL rendering, alpha-beta AI, A* pathfinding, and networking.}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
